Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-05-09 manuscript.Rmd
Force install tinytex if not present
Update manuscript.Rmd

\vspace{10mm}
\begin{center}
Lusine Grigoryan$^{1}$, Vladimir Ponizovskiy$^{2}$, Marie Isabelle Wießflog$^{2}$, Evgeny Osin$^{3}$,$^{4}$, and Brian Lickel$^{5}$
\vspace{30mm}

@@

# download latex if not already present
if (!tinytex::is_tinytex()){tinytex::install_tinytex()}

>>>>

\vspace{10mm}
\begin{center}
Lusine Grigoryan$^{1}$, Vladimir Ponizovskiy$^{2}$, Marie Isabelle Wießflog$^{2}$, Evgeny Osin$^{3,4}$, and Brian Lickel$^{5}$
\vspace{30mm}

@@

# download latex if not already present
if (!tinytex::is_tinytex()){tinytex::install_tinytex(force = TRUE)}
